National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2020-11-29 Manuscript_Bayesian.Rmd
fixed equation

keywords          : "Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being"
wordcount         : "5181 words in text body, 1191 words in reference section"
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
figsintext        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
extra_dependencies: ["rotating", "booktabs", "graphicx","longtable","amsmath","amsfonts","amssymb"]

@@

The deterministic portion of both the Personal Wellbeing and the Life Satisfaction models is as follows: 
$$
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ +  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{6}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
$$
\newpage

>>>>

keywords          : "Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being"
wordcount         : "5181 words in text body, 1191 words in reference section"
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
figsintext        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
extra_dependencies: ["rotating", "booktabs", "graphicx","longtable","amsmath","amsfonts","amssymb"]

@@

The deterministic portion of both the Personal Wellbeing and the Life Satisfaction models is as follows: 
$$
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\  + \\
& \quad  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
&\quad \beta_{4}(\operatorname{Age in Decades (C)})\  +\\ 
& \quad  \beta_{5}(\operatorname{Ethnicity}_{\operatorname{Maori}})\ +\\
&\quad \beta_{6}(\operatorname{Ethnicity}_{\operatorname{Pacific}})\ +  \\ 
& \quad  \beta_{7}(\operatorname{Ethnicity}_{\operatorname{Asian}})\ +\\
& \quad \beta_{8}(\operatorname{Male} )+ \\ 
& \quad \beta_{9}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{10}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{11}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
$$
\newpage

### 2020-11-29 Manuscript_Bayesian.tex
fixed equation

The deterministic portion of both the Personal Wellbeing and the Life Satisfaction models is as follows:
\[
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ +  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{6}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
\]
\newpage

>>>>

The deterministic portion of both the Personal Wellbeing and the Life Satisfaction models is as follows:
\[
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\  + \\
& \quad  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
&\quad \beta_{4}(\operatorname{Age in Decades (C)})\  +\\ 
& \quad  \beta_{5}(\operatorname{Ethnicity}_{\operatorname{Maori}})\ +\\
&\quad \beta_{6}(\operatorname{Ethnicity}_{\operatorname{Pacific}})\ +  \\ 
& \quad  \beta_{7}(\operatorname{Ethnicity}_{\operatorname{Asian}})\ +\\
& \quad \beta_{8}(\operatorname{Male} )+ \\ 
& \quad \beta_{9}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{10}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{11}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
\]
\newpage

### 2020-11-29 Supplement_And_Analysis.Rmd
fixed equation

\[
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ +  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{6}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
\]

>>>>

\[
\begin{aligned}
& \quad  \boldsymbol{b} = \\
& \quad \beta_{1}(\operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\
&\quad \beta_{2}(\operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\  + \\
& \quad  \beta_{3}(\operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}})\ +\\
&\quad \beta_{5}(\operatorname{Age in Decades (C)})\  +\\ 
& \quad  \beta_{6}(\operatorname{Ethnicity}_{\operatorname{Maori}})\ +\\
&\quad \beta_{7}(\operatorname{Ethnicity}_{\operatorname{Pacific}})\ +  \\ 
& \quad  \beta_{8}(\operatorname{Ethnicity}_{\operatorname{Asian}})\ +\\
& \quad \beta_{4}(\operatorname{Male} )+ \\ 
& \quad \beta_{4}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{SpiritExcludesGod}})\ + \\ 
& \quad \beta_{5}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodAndSpirit}})\ + \\
&\quad \beta_{6}(\operatorname{Years} \times \operatorname{Beliefs}_{\operatorname{GodExcludesSpirit}}) \\ 
\end{aligned}
\]
